### 2016-09-23 assumptions.tex
Simplify some wording

\texttt{None} represents the
``unknown'' case. This could mean that given assumptions do not unambiguously
specify the truth of an attribute. For instance,
\texttt{Symbol(\textquotesingle{}x\textquotesingle{}, real=True).is\_positive}
will give \texttt{None} because a real symbol might be positive or negative.
The \texttt{None} could also mean that not enough is known or implemented to
compute the given fact. For instance, \texttt{(pi + E).is\_irrational} gives
\texttt{None}---indeed, determining whether $\pi + e$ is rational or irrational
is an open problem in mathematics~\cite{lang1966introduction}.

>>>>

\texttt{None} represents the ``unknown'' case. This could mean that given
assumptions do not unambiguously specify the truth of an attribute. For
instance, \texttt{Symbol(\textquotesingle{}x\textquotesingle{},
  real=True).is\_positive} will give \texttt{None} because a real symbol might
be positive or negative. The \texttt{None} could also mean that not enough is
known or implemented to compute the given fact. For instance, \texttt{(pi +
  E).is\_irrational} gives \texttt{None}---indeed, the rationality of
$\pi + e$ is an open problem in mathematics~\cite{lang1966introduction}.
